ActiveCA: an open data product on active transportation episodes in Canada

### 2024-11-13 Data-Paper/Manuscript-Data-Package.Rmd
Data paper
adjusting legend on manuscript

```{r figure-01, echo=FALSE, out.width="100%", fig.cap="Percentage of walking Trips Categorized by Origin and Destination", fig.align="center"}

@@

```{r  figure-02, echo=FALSE, out.width="100%", fig.cap="Percentage of walking Trips Categorized by Origin and Destination", fig.align="center"}

@@

```{r figure-03, echo=FALSE, out.width="100%", fig.cap=paste0("Percentage of walking Trips Categorized by Origin and Destination", mode), fig.align="center"}

>>>>

```{r figure-01, echo=FALSE, out.width="100%", fig.cap="Percentage of walking trips categorized by origin and destination", fig.align="center"}

@@

```{r  figure-02, echo=FALSE, out.width="100%", fig.cap="Percentage of cycling trips categorized by origin and destination", fig.align="center"}

@@

```{r figure-03, echo=FALSE, out.width="100%", fig.cap=paste0("Empirical data and impedance functions fitted for walking trips with `work or school` as destination."), fig.align="center"}

### 2024-11-13 Data-Paper/Manuscript-Data-Package.tex
Data paper
adjusting legend on manuscript

\caption{Percentage of walking Trips Categorized by Origin and Destination}\label{fig:figure-01}
\end{figure}

@@

\caption{Percentage of walking Trips Categorized by Origin and Destination}\label{fig:figure-02}
\end{figure}

@@

\caption{Percentage of walking Trips Categorized by Origin and DestinationWalking}\label{fig:figure-03}
\end{figure}

>>>>

\caption{Percentage of walking trips categorized by origin and destination}\label{fig:figure-01}
\end{figure}

@@

\caption{Percentage of cycling trips categorized by origin and destination}\label{fig:figure-02}
\end{figure}

@@

\caption{Empirical data and impedance functions fitted for walking trips with `work or school` as destination.Walking}\label{fig:figure-03}
\end{figure}
